---
title: "HW_Unit5_KHenley"
author: "Kris Henley"
date: "October 8, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1.A.  
Importing yob2016.txt and creating an object called df that consists
of 3 columns with human readable column names.
```{r, echo=TRUE}
df <- read.table("C:/Users/henlek1/Desktop/yob2016.txt", header = FALSE, sep=";", col.names= c("Name", "Gender","Total"))
```

Question 1.B.  
Display the summary and structure of df
```{r, echo=TRUE}
head(df)
summary(df)
str(df)
```
Question 1.C. 
Your client tells you that there is a problem with the raw file. One name was entered twice and misspelled. The client cannot remember which name it is; there are thousands he saw! But he did mention he accidentally put three y's at the end of the name. Write an R command to figure out which name it is and display it.
```{r, echo=TRUE}
subset(df,grepl("^.+(yyy)$",Name))
```

Question 1.D. 
Upon finding the misspelled name, please remove this particular observation, as the client says it's redundant. Save the remaining dataset as an object: y2016
```{r, echo=TRUE}
y2016 <- df[-212,]
str(y2016)
```

Question 2.A. 
Utilize yob2015.txt for this question.
Like 1a, please import the .txt file into R. Look at the file before you do. YouXmight have to change some options to import it properly. Again, please give the dataframe human-readable column names. Assign the dataframe to y2015.
```{r, echo=TRUE}
y2015 <- read.table("C:/Users/henlek1/Desktop/yob2015.txt", header = FALSE, sep=",", col.names= c("Name", "Gender","Total"))
```

Question 2.B. 
Display the last ten rows in the dataframe. Describe something you find interesting about these 10 rows.
```{r, echo=TRUE}
tail(y2015,10)
```
*Something interesting to note would be these names starting with "Z" each had 5
children given each respectively.

Question 2.C. 
Merge y2016 and y2015 by your Name column; assign it to final. The client only cares about names that have data for both 2016 and 2015; there should be no NA values in either of your amount of children rows after merging.
```{r, echo=TRUE}
final <- merge(x=y2016, y=y2015, by= "Name")
summary(final)
```

Question 3.A. 
Utilize your data frame object final for this part.
Create a new column called "Total" in final that adds the amount of children in 2015 and 2016 together. In those two years combined, how many people were given popular names?
**Note:  Since I have a column called 'Total' already I'll call this one "Gtotal"
```{r, echo=TRUE}
final$GTotal <- final$Total.x + final$Total.y
summary(final)
```
I'm not sure how we are definining "popular" in order to provide an accurate total 
how many people were given "popular" names in both years together, but if we take
the top ten total as we retreived for 2.B then 343,758 were named from the top 10
list and thus given "popular" names in 2015 and 2016.


Question 3.B.
Sort the data by Total. What are the top 10 most popular names?
```{r, echo=TRUE}
library(dplyr)
top_n(final, 10, GTotal)
```
Top 10 names in 2015-2016 both genders:  Ava,Emma,Isabella,Jacob,Liam,Mason,Noah,
Olivia,Sophia,William

Question 3.C.
The client is expecting a girl! Omit boys and give the top 10 most popular girl's names.
```{r, echo=TRUE}
TopGirls <- filter(final, Gender.x=="F" & Gender.y=="F")
top_n(TopGirls, 10, GTotal)
```

Question 3.D.
Write these top 10 girl names and their Totals to a CSV file. Leave out the other columns entirely.
```{r, echo=TRUE}
TopGirlsNames <- top_n(TopGirls, 10, GTotal)
write.csv(TopGirlsNames[-c(2:5)], file = "TopGirlsNames.csv")
```

Question 4
Upload to GitHub (10 points)

Repo URL:  https://github.com/kristopher33/SMU_MSDS_HW/tree/master/HW_MSDS_SMU/DDS_HW


